---
title: Misc stuff
author: Jun
output: html_document
---
```{r include = FALSE}
# import libraries
library(DT)
library(dplyr)
library(vroom)
```

## Notes:

## Steps:

## Todo:

## Info:



## EDA
spit out formatted names for DQMWG

input: 1 vectors, present, strings. 
fn: already has ordered factors as source of truth. Any not in vector is not
    present. Sort
output: return 2 vectors(in lists?), ordered, present, not present
```{r}

ordered <- c("Michael Thompson"
, "Miranda Li"
, "Alein Chun"
, "Paul Bouganim"
, "Joanne Chiu"
, "Marco Cifuentes"
, "Donell Cohen"
, "Donald Davies"
, "Tod Davis"
, "Rachel Fridman"
, "Jessica Hermosura"
, "Ha Hoang"
, "Jessica Hopkins"
, "Andrew Hudson"
, "Jennifer Kegle"
, "Mandy Law-Huang"
, "Walter Liem"
, "Susan Mangeno"
, "Julian Martinez"
, "Lilly Martirosyan"
, "Shad Nicks"
, "Soshi Odawara"
, "Ted Rafdal"
, "Dexter Reinoso"
, "Marcus Harrison"
, "Ron Ruckle"
, "Rachel Selmont"
, "Colleen Stalvey"
, "Susan Tiffany"
, "Eduardo Genao"
, "Hudson Stuck"
, "Erin Joyce"
, "Van Vu"
, "Michelle Fang"
, "Denise Abcede"
, "Jun Hernandez"
)

# can't have typos
# TODO: have typos outputted 
present <- c("Miranda Li", "Eduardo Genao", "Susan Tiffany", "Alein Chun",
             "Dexter Reinoso", "Donald Davies", "Erin Joyce", "Hudson Stuck",
             "Julian Martinez", "Jun Hernandez", "Mandy Law-Huang", 
             "Marco Cifuentes", "Marcus Harrison", "Michelle Fang", 
             "Michael Thompson", "Donell Cohen", "Rachel Fridman", "Soshi Odawara",
             "Ted Rafdal", "Van Vu", "Denise Abcede")

sorted <- (present[order(match(present, ordered))]) 
absent <- setdiff(ordered, sorted)
out <- c(paste(sorted, collapse = ", "), paste(absent, collapse = ", "))



# TODO: test ordered arg ctor
sort_names <- function(present, ordered = c()) {
    # proper order
    ordered <- c("Michael Thompson", "Miranda Li", "Alein Chun", "Paul Bouganim", 
                 "Joanne Chiu", "Marco Cifuentes", "Donell Cohen", "Donald Davies", 
                 "Tod Davis", "Rachel Fridman", "Jessica Hermosura", "Ha Hoang", 
                 "Jessica Hopkins", "Andrew Hudson", "Jennifer Kegle", "Mandy Law-Huang",
                 "Walter Liem", "Susan Mangeno", "Julian Martinez", "Lilly Martirosyan",
                 "Shad Nicks", "Soshi Odawara", "Ted Rafdal", "Dexter Reinoso",
                 "Marcus Harrison", "Ron Ruckle", "Rachel Selmont", "Colleen Stalvey", 
                 "Susan Tiffany", "Eduardo Genao", "Hudson Stuck", "Erin Joyce", 
                 "Van Vu", "Michelle Fang", "Denise Abcede", "Jun Hernandez"
    )
    sorted <- (present[order(match(present, ordered))]) 
    absent <- setdiff(ordered, sorted)

    out <- c(paste(sorted, collapse = ", "), paste(absent, collapse = ", "))
    out
}

# unit test
got <- sort_names(present)

# write want, got





```

Michael Thompson, Miranda Li, Alein Chun, Marco Cifuentes, Donell Cohen, Donald Davies, Rachel Fridman, Mandy Law-Huang, Julian Martinez, Soshi Odawara, Ted Rafdal, Dexter Reinoso, Marcus Harrison, Susan Tiffany, Eduardo Genao, Hudson Stuck, Erin Joyce, Van Vu, Michelle Fang, Denise Abcede, Jun Hernandez"

Paul Bouganim, Joanne Chiu, Tod Davis, Jessica Hermosura, Ha Hoang, Jessica Hopkins, Andrew Hudson, Jennifer Kegle, Walter Liem, Susan Mangeno, Lilly Martirosyan, Shad Nicks, Ron Ruckle, Rachel Selmont, Colleen Stalvey


testing out image recognition with tesseract
```{r}
library(tesseract)
eng <- tesseract("eng")
text <- tesseract::ocr("http://jeroen.github.io/images/testocr.png", engine = eng)
cat(text)

att1<- tesseract::ocr("att1_51722.PNG", engine = eng)
att2<- tesseract::ocr("att2_51722.PNG", engine = eng)
cat(att1)
cat(att2)

length(att1)


```
omg this actually works 













